### 2016-12-23 analysis-note-vf/analysis-2.tex
update the analysis note with the latest plots for both DVCS channels
update the note with the final tables and texting

\item Cone angle cut between the measured real photon and the missing particle 
   in the $e^{4}HeX$ configuration. It is defined as:
\begin{equation}
\theta(\gamma, e^{4}HeX) = cos^{-1} \left( 
\frac{\overrightarrow{\mathbf{P}}_{\gamma} \cdot 
\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}}{|\overrightarrow{\mathbf{P}}_{\gamma^{}}| 
|\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}|}   \right).
\end{equation}
\end{itemize}
Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  
In these plots, the blue distributions represent the coherent events after the 
DVCS characteristic cuts and before all the exclusivity cuts. The shaded 
distributions stand for the events which passed all the exclusivity cuts except 
the one on the quantity plotted. We fitted each shaded distribution by a 
Gaussian and then we applied  3$\sigma$ cuts around the mean value of each 
distribution. The events which pass these cuts are assumed to be good $^{4}He$ 
DVCS events.

\begin{figure}[!h]
\centering
\includegraphics[scale=0.4]{fig_dvcs/all_coh_exc_cuts.png}
\caption{The coherent DVCS exclusivity cuts. The blue distributions represent 
   the coherent DVCS events candidate. The shaded distributions represent the 
   events which passed all the exclusivity cuts except the quantity plotted.  
   The vertical red lines represent $3\sigma$ cuts. The missing momentum in $x$ 
   and $y$ directions in the configuration $e^{4}He\gamma X$, are shown for 
information. The mean and the sigma values of each quantity can be found in 
Appendix \ref{exclusivity_cuts}, table \ref{Table:coh_exclusivity_cuts}.} 
\label{fig:coh_exclusivty_cuts}
\end{figure}

@@

%\paragraph{$\blacklozenge$ Exclusivity cuts}~
%~~~~The exclusivity of the proton DVCS events is ensured by applying the following set of cuts:
%\begin{itemize}
%\item The coplanarity cut ($\Delta \phi$) between the recoil proton and the final state real photon. 
%\item Missing energy, mass and transverse momentum ($p_{T} = \sqrt{p^{2}_{x} + p^{2}_{y}}$) cuts in the final state configuration $ep\gamma X$.
%\item Missing mass cuts in the final state configurations $epX$ and $e\gamma X$.
%\item Cone angle cut between the measured real photon and the missed particle in the %configuration $epX$.
%\end{itemize}
\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{fig_dvcs/all_incoh_exc_cuts.png}
\caption{The incoherent DVCS exclusivity cuts. The blue distributions represent 
   all the events with one good electron, one good proton, and at least one 
   photon in the IC. The shaded brown distributions show the incoherent DVCS 
   events which passed all the exclusivity cuts except the one on the quantity 
   drawn. The distributions from left to right and from top to bottom are: the 
   proton-photon coplanarity, the missing energy, missing mass squared, missing 
   transverse momentum from $ep\gamma X$, the missing mass squared $epX$ and 
   the missing mass squared $e\gamma X$, the angle between the missing particle 
   in $epX$ and the measured photon, the missing $P_{x}$ and $P_{y}$ in 
   $ep\gamma X$. The vertical red lines represent 3$\sigma$ cuts. The mean and 
   sigma values of each shaded distribution are listed in table 
\ref{Table:incoh_exclusivity_cuts}.} \label{fig:incoh_exclusivty_cuts}
\end{figure}

>>>>

\item Cone angle cut between the measured real photon and the missing particle 
   in the $e^{4}HeX$ configuration. It is defined as:
\begin{equation}
\theta(\gamma, e^{4}HeX) = cos^{-1} \left( 
\frac{\overrightarrow{\mathbf{P}}_{\gamma} \cdot 
\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}}{|\overrightarrow{\mathbf{P}}_{\gamma^{}}| 
|\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}|}   \right).
\end{equation}
\end{itemize}
Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  In 
these plots, the black distributions represent the coherent events after the 
DVCS characteristic cuts and before all the exclusivity cuts. The shaded 
distributions stand for the events which passed all the exclusivity cuts except 
the one on the quantity plotted. We fitted each shaded distribution by a 
Gaussian and then we applied  3$\sigma$ cuts around the mean value of each 
distribution except the missing energy distribution for which a final 
[-0.45:0.5] GeV cut is applied to remove the tails and reduce the background.   
The events which pass these cuts are assumed to be good $^{4}He$ DVCS events.

\begin{figure}[!h]
\centering
\includegraphics[scale=0.9]{fig_Dec2016/all_coh_exc_cuts.pdf}
\caption{The coherent DVCS exclusivity cuts. The blue distributions represent 
   the coherent DVCS events candidate. The shaded distributions represent the 
   events which passed all the exclusivity cuts except the quantity plotted.  
   The vertical red lines represent $3\sigma$ cuts on all the distribution 
   except the missing energy distribution for which [-0.45:0.5] GeV cut is 
   applied.  The missing momentum in $x$ and $y$ directions in the 
configuration $e^{4}He\gamma X$, are shown for information. The mean and the 
sigma values of each quantity can be found in Appendix \ref{exclusivity_cuts}, 
table \ref{Table:coh_exclusivity_cuts}.} \label{fig:coh_exclusivty_cuts}
\end{figure}

@@

%\paragraph{$\blacklozenge$ Exclusivity cuts}~
%~~~~The exclusivity of the proton DVCS events is ensured by applying the following set of cuts:
%\begin{itemize}
%\item The coplanarity cut ($\Delta \phi$) between the recoil proton and the final state real photon. 
%\item Missing energy, mass and transverse momentum ($p_{T} = \sqrt{p^{2}_{x} + p^{2}_{y}}$) cuts in the final state configuration $ep\gamma X$.
%\item Missing mass cuts in the final state configurations $epX$ and $e\gamma X$.
%\item Cone angle cut between the measured real photon and the missed particle in the %configuration $epX$.
%\end{itemize}
\begin{figure}[h!]
\centering
\includegraphics[scale=0.9]{fig_Dec2016/all_incoh_exc_cuts.pdf}
\caption{The incoherent DVCS exclusivity cuts. The black distributions 
   represent all the events with one good electron, one good proton, and at 
   least one photon in the IC. The shaded brown distributions show the 
   incoherent DVCS events which passed all the exclusivity cuts except the one 
   on the quantity drawn. The distributions from left to right and from top to 
   bottom are: the proton-photon coplanarity, the missing energy, missing mass 
   squared, missing transverse momentum from $ep\gamma X$, the missing mass 
   squared $epX$ and the missing mass squared $e\gamma X$, the angle between 
   the missing particle in $epX$ and the measured photon, the missing $P_{x}$ 
   and $P_{y}$ in $ep\gamma X$. The vertical red lines represent 3$\sigma$ 
   cuts. The mean and sigma values of each shaded distribution are listed in 
table \ref{Table:incoh_exclusivity_cuts}.} \label{fig:incoh_exclusivty_cuts}
\end{figure}

### 2016-12-23 analysis-note-vf/data_analysis.tex
update the note with the final tables and texting

\begin{itemize}
\item Negative charge: the torus magnet generates a field which has mainly azimuthal components. Hence, the trajectory of a negative particle will be bent towards the beam line direction without changing azimuth. Consequently, information on its charge is accessible from the curvature of its trajectory.

@@

\item Track helix-fit quality: figure \ref{fig:rtpc_X2} shows the $\chi^{2}$ 
   distributions for the positive tracks originating within the RTPC. We apply 
   $\chi^{2}$~<~3.5 to select good $^4$He tracks.

@@

\begin{figure}[tbp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_z.png}
\caption{ $z$-vertices for the reconstructed positive tracks with respect to 
the RTPC center (-64 cm with respect to the CLAS center), in the two modules of 
the RTPC. We chose the cut -80  mm < z < 80 mm to select good tracks.} 
\label{fig:rtpc_z}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_X2.png}
\caption{$\chi^{2}$ distribution for the tracks in the two modules of the RTPC, with the cut we require to select good tracks: $\chi^{2}$ < 3.5.}
\vspace{0.5in}
\label{fig:rtpc_X2}
\end{minipage}
\end{figure}

\begin{figure}[tbp]
\vspace{-0.3in}
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_sdist.png}
\caption{$sdist$ distribution for the positive tracks in the RTPC. $|sdist|$~<~2.0 mm cut is applied to select good tracks.} 
\label{fig:rtpc_sdist}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_edist.png}
\caption{$edist$ distribution for the positive tracks in the RTPC. We require $-1.0$~mm~<~$edist$~<~5.0 mm to select good tracks.}
\label{fig:rtpc_edist}
\end{minipage}
\end{figure}

>>>>

\begin{itemize}

\item Negative charge: the torus magnet generates a field which has mainly 
   azimuthal components. Hence, the trajectory of a negative particle will be 
   bent towards the beam line direction without changing azimuth.  
   Consequently, information on its charge is accessible from the curvature of 
   its trajectory.

@@

\item Track helix-fit quality: figure \ref{fig:rtpc_X2} shows the $\chi^{2}$ 
   distributions for the positive tracks originating within the RTPC. We apply 
   $\chi^{2}$~<~3.0 to select good $^4$He tracks.

@@

\begin{figure}[tbp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_z.png}
\caption{ $z$-vertices for the reconstructed positive tracks with respect to 
the RTPC center (-64 cm with respect to the CLAS center), in the two modules of 
the RTPC. We chose the cut -80  mm < z < 80 mm to select good tracks.} 
\label{fig:rtpc_z}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_X2.png}
\caption{$\chi^{2}$ distribution for the tracks in the two modules of the RTPC, 
with the cut we require to select good tracks: $\chi^{2}$ < 3.}
\vspace{0.5in}
\label{fig:rtpc_X2}
\end{minipage}
\end{figure}

\begin{figure}[tbp]
\vspace{-0.3in}
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_sdist.png}
\caption{$sdist$ distribution for the positive tracks in the RTPC.  
-3~<~$sdist$~<~2.0 mm cut is applied to select good tracks.} 
\label{fig:rtpc_sdist}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_edist.png}
\caption{$edist$ distribution for the positive tracks in the RTPC. We require 
$-2.0$~mm~<~$edist$~<~3.0 mm to select good tracks.}
\label{fig:rtpc_edist}
\end{minipage}
\end{figure}
